### 2016-02-10 pdocs/thesis/bullet-plasticity.tex
pdocs charpy-results

>>>>

\subsection{Results for hinge constraint with motors}
Results are very good although sensitive to parameters changes. Energy loss is in right scale. 
Specimen bends and keeps deformed shape.

\subsection{Results for plasticHingeConstraint}
Results are quite similar as for hinge constraint with motors. 
Breaking point can be configured based on rotation angle which makes material behaviour more realistic.

\subsection{Results for elasticPlasticConstraint}
Results are quite similar as for plasticHingeConstraint as this case is dominated by plastic bending.
Additional logic helps to avoid stablity issues.

\subsection{Results for elasticPlastic2Constraint}
Results are quite similar as for elasticPlasticConstraint and this constraint seems to best candidate for further development.
Table \ref{tab:ep2ts} shows energy loss for few timesteps as example to demonstrate sensitivity of solution.

\begin {table}[htb!]
\begin{center}
\begin{tabular}{| c| c|}
\hline
{\bf Timestep[ms]} & {\bf Energy loss [J]}\\  \hline
 0.100001 &  120 \\ \hline
 0.1 &  110 \\ \hline
 0.09999 &  140 \\ \hline
 0.08 &  170 \\ \hline
 0.05 &  215 \\ \hline
\end {tabular}
\end{center}
\caption {Energy loss for few timesteps} \label{tab:ep2ts} 
\end {table}

### 2016-02-10 pdocs/thesis/discussion.tex
pdocs
pdocs charpy-results

@@

Current implementation is done based on \bullet but it still needs refactoring and testing before it can be 
accepted to main stream. Interfaces should be reafctored so that handling of additional features like large 
displacements and material nonlinearity can be implemented without further changes.

@@

Update of constraints can be done in  many ways but using callbacks allows clean integration i.e. no changes
to solver core are needed.
In \bullet there are already three per step callbacks.

@@

\subsubsection{Material nonlinearity}
Update of constraint properties can be done in callbacks in similar way as for large displacements.
Material definition should be defined so that stress-strain curve can be defined as array of pairs.

>>>>

\subsubsection{Implementation using GPU}
\bullet\ can already utilize GPU for many operations. 
Analysis on possible issues in used interfaces should be done before integrations.

@@

Current implementation is done based on \bullet\ but it still needs refactoring and testing before it can be 
accepted to main stream. Interfaces should be reafctored so that handling of additional features like large 
displacements and material nonlinearity can be implemented without further changes.

@@

Update of constraints can be done in  many ways but using callbacks allows clean integration i.e. no changes
to solver core are needed.
In \bullet\ there are already three per step callbacks.

@@

\subsubsection{Material nonlinearity}
Update of constraint properties can be done in callbacks in similar way as for large displacements.
Material definition should be defined so that stress-strain curve can be defined as array of pairs.
This is probably not significant feature for simulations in gaming area but interesting feature for research and teaching area.

\subsection{Object subdivision just in time}
Just in time activation could avoid extra overhead from multiple objects and constraints.
Impacts causing plasticity are usually quite brief and they happen at distinct times. 
Simulation could allocate processing units for handling these and release them after impact has been processed.
